### 2016-01-24 featureImagesTable.tex
ENH:  more stuff.

\begin{table}[!htb]
  \centering
  \begin{tabular*}{0.65\textwidth}{@{\extracolsep{\fill}} ll}
    \multicolumn{1}{c}{\textbf{Feature type}} & \multicolumn{1}{c}{\textbf{Image source}} \\
    \toprule
    \midrule
    \multicolumn{2}{c}{\textbf{Intensities}} \\
    \midrule
    normalized/preprocessed & FLAIR, T1, and T2 \\
    \midrule
    \multicolumn{2}{c}{\textbf{Symmetric template}} \\
    \midrule
    template difference & FLAIR, T1, and T2 \\
    contralateral difference & FLAIR, T1, and T2 \\
    location indices & FLAIR, T1, and T2 \\
    \midrule
    \multicolumn{2}{c}{\textbf{Segmentation probabilities}} \\
    \midrule
    $Pr$(cerebrospinal fluid) & T1 \\
    $Pr$(gray matter) & T1 \\
    $Pr$(white matter) & T1 \\
    $Pr$(deep bray matter) & T1 \\
    $Pr$(brain stem) & T1 \\
    $Pr$(cerebellum) & T1 \\
    \midrule
    \multicolumn{2}{c}{\textbf{Distance maps}} \\
    \midrule
    cerebrospinal fluid & T1 brain segmentation \\
    gray matter & T1 brain segmentation \\
    deep gray matter & T1 brain segmentation \\
    whole brain & T1 brain segmentation \\
    \midrule
    \multicolumn{2}{c}{\textbf{Neighborhood statistics}} \\
    \midrule
    mean & FLAIR, T1, and T2 \\
    standard deviation & FLAIR, T1, and T2 \\
    skewness & FLAIR, T1, and T2 \\
    \midrule
    \bottomrule
  \end{tabular*}
 \label{table:indices}
 \caption{List of feature images used for Stage 1 of the proposed white matter
          hyperintensity segmentation framework.}
\end{table}

>>>>

\begin{table}[!htb]
  \centering
  \begin{tabular*}{0.65\textwidth}{@{\extracolsep{\fill}} ll}
    \multicolumn{1}{c}{\textbf{Feature type}} & \multicolumn{1}{c}{\textbf{Image source}} \\
    \toprule
    \midrule
    \multicolumn{2}{c}{\textbf{Intensities}} \\
    \midrule
    normalized/preprocessed & FLAIR, T1, and T2 \\
    \midrule
    \multicolumn{2}{c}{\textbf{Symmetric template}} \\
    \midrule
    template difference & FLAIR, T1, and T2 \\
    contralateral difference & FLAIR, T1, and T2 \\
    location indices & FLAIR, T1, and T2 \\
    \midrule
    \multicolumn{2}{c}{\textbf{Segmentation probabilities}} \\
    \midrule
    $Pr$(cerebrospinal fluid) & T1 \\
    $Pr$(gray matter) & T1 \\
    $Pr$(white matter) & T1 \\
    $Pr$(deep gray matter) & T1 \\
    $Pr$(brain stem) & T1 \\
    $Pr$(cerebellum) & T1 \\
    \midrule
    \multicolumn{2}{c}{\textbf{Distance maps}} \\
    \midrule
    cerebrospinal fluid & T1 brain segmentation \\
    gray matter & T1 brain segmentation \\
    deep gray matter & T1 brain segmentation \\
    whole brain & T1 brain segmentation \\
    \midrule
    \multicolumn{2}{c}{\textbf{Neighborhood statistics}} \\
    \midrule
    mean & FLAIR, T1, and T2 \\
    standard deviation & FLAIR, T1, and T2 \\
    skewness & FLAIR, T1, and T2 \\
    \midrule
    \bottomrule
  \end{tabular*}
 \label{table:indices}
 \caption{List of feature images used for Stage 1 of the proposed white matter
          hyperintensity segmentation framework.}
\end{table}

### 2016-01-24 methods.Rmd
ENH:  more stuff.

Feature generation for the proposed framework is critical. The performance of the selected
machine learning strategy is limited by the input used for training. The image features
described below were selected based on previous work in the literature and our own observations
regarding tumor characteristics and what could possibly be encoded algorithmically.
Observations regarding tumor intensity differences from normal tissue has been encoded in
previously proposed research by calculating normalized neighborhood intensity statistics
and intensity modeling (e.g., Bauer et al. 2011, 2012; Geremia et al. 2012; Zikic et al.
2012). In these approaches both the features and classification algorithm are limited to
voxelwise considerations.

Our success in the MICCAI 2013 challenge was largely due to the inclusion of an extremely
important set of features based on the common observation of bilateral asymmetrization
caused by tumor presence. Additionally, several features were designed to encode spatial
coherence even though the RF classification is performed on a voxelwise basis. For example,
connected component geometry of the intensity modeling labels were used to discriminate
observations of compact, isotropic objects (vs. highly anisotropic) typical of tumor
presence and growth (Greenspan 1972). Table 1 provides a listing of image features used
and the motivation for their inclusion.

@@

>>>>

## Imaging

## Quantitative analysis

Machine learning and pattern recognition techniques have proven extremely useful
for various medical image analysis workflows (see, for example, the annual
Workshop on Machine Learning in Medical Imaging held in conjunction with the Medical
Image Computing and Computer-Aided Intervention international meeting [@mlmi2015]).
Popular techniques such as support vector machines and neural networks have been applied
successfully to clinically relevant imaging tasks such as segmentation
(e.g., [@Bauer:2011aa]) and diagnostic prediction (e.g., [@Tong:2014aa;@Liu:2013aa]).

Another versatile technique that has acheieved much success

The random forest machine learning framework provides an excelllent fromework for medical
image segmentation

Supervised methodologies are uniquely characterized, in part, by the feature images that
are used to identify the regions of interest.

Intensity information alone is insufficient for removing false positives.  For example,
as pointed out in [@Neema:2009aa], higher intensities can be found at the periventricular
caps in normal subjects which often confounds automated lesion detection algorithms.

@@

![Representation of Stage 1 feature images for subject 01C1019.  Input for each
subject consists of FLAIR, T1-, and T2-weighted images which are rigidly pre-aligned
[@Avants:2014aa] to the
space of the T1 image.  The three images are then preprocessed (N4 bias correction
[@Tustison:2010ac] and denoising [@Manjon:2010aa]) followed by application of standard ANTs
brain extraction and $n$-tissue segmentation protocols using the MMRR
symmetric template corresponding and priors [@Tustison:2014ab] to the T1 image.  The
feature images are then generated for voxelwise input to the RF model which results in
the voting maps illustrated on the right which gives a probabilistic classification of
tissue type.
](Figures/featureImages.png)

\clearpage

# References
